---
title: "paper in workshop"
author: "Hye-Rim Hong"
date: "2023-01-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages}
library(tidyverse)
```

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r read-data}
gapminder_1997 <- read_csv("data/gapminder_1997.csv")

```
```{r gdp-lifeExp-1997-plot}
#make plot of GDP (x-axis) vs lifeExp(y-axis)

ggplot(gapminder_1997, aes(x = gdpPercap, y = lifeExp))+
 geom_point()+
labs(x = "GDP Per Capita", y = "Life expectancy")+
theme_classic()
  

```


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
